A data-intensive assessment of the species-abundance distribution.

### 2015-04-03 defense_pres.tex
Changes some figures, adds some figures.

\subsection{Best practices}
\begin{frame}[t]
\frametitle{Best practice recommendations}
\begin{itemize}
\item Test multiple models with consistent statistical approach.
\item Test with multiple taxonomic groups/ecosystems.  
\end{itemize}
\begin{center}
\includegraphics[scale=.2]{./sad-data/dissertation/SpatialTaxonomic.png}
\end{center}
\end{frame}

\section{Data}
\subsection{Current Data}
\begin{frame}[t]
\frametitle{Current Data}
\vspace{-7pt}
\includegraphics[scale=.55]{./sad-data/chapter3/presentation_map.png}
\note{
\begin{large}
Major macroecological datasets\\
\end{large}
\begin{itemize}
\item Largely terrestrial
\item Largely North American
\item Many publicly available, some not.
\end{itemize}
~\\
~\\
~\\
~\\
\begin{large}
Lots of data in the literature.\\
\end{large}}
\end{frame}

@@

\subsubsection{Data Collection}
\begin{frame}[t]{}
\frametitle{Data}
Inclusion criteria:
\begin{itemize}
\item Quantitative abundances
\item Animals
\item Complete sampling
\item Must not be heavily summarized or processed
\item High degree of taxonomic resolution
\item Observational
\end{itemize}
\end{frame}

\begin{frame}[shrink=30]
\frametitle{Data}
\begin{table}
\begin{tabular}{l} 
 Variables collected\\ 
\hline
\\
 Class \\
 Family\\
 Genus \\
 Species (Specific epithet)\\
 Relative abundance \\
 Abundance \\
 Collection Year, starting\\
 Collection Year, ending \\
 Site Name \\
 Biogeographic region \\
 Site notes\\ 
\end{tabular}
\caption{List of variables collected.}
\end{table}
\end{frame}

@@

\subsubsection{Data Summary}
\begin{frame}{}
\frametitle{Data}
\includegraphics[scale=.35]{../Miscellaneous/Pictures/Phd/CompiledData.png}
\end{frame}

\begin{frame}{}
\frametitle{Data}
\includegraphics[scale=.27]{./sad-data/dissertation/bioregions.png}
\end{frame}

\begin{frame}{}
\frametitle{Data}
\includegraphics[scale=.45]{./sad-data/dissertation/taxa_sites.png}
\end{frame}

\begin{frame}{}
\frametitle{Data}
\includegraphics[scale=.45]{./sad-data/dissertation/num_taxa.png}
\end{frame}

@@

@@

\subsubsection{Data}
\begin{frame}{}
\frametitle{Data}
\includegraphics[scale=.4]{../Miscellaneous/Pictures/Phd/MapCreatures.png}
\end{frame}

@@

\subsection{Conclusions}
\begin{frame}
\frametitle{Neutral analysis}
Difficult to identify a clear winning model.
\begin{itemize}
\item Results consistent with our species abundance distribution model comparisons. 
\item Results different from Connolly et al. 2014.
\begin{itemize}
\item Non-neutral model outperforms the neutral model in marine systems.
\item Our results suggest marine systems more generally approximated by non-neutral dynamics; terrestrial systems more variable between neutral and non-neutral dynamics.
\end{itemize}
\end{itemize}
\end{frame}

>>>>

\subsection{Best practices}
\begin{frame}[t]
\frametitle{Best practice recommendations}
\begin{itemize}
\item Test multiple models with consistent statistical approach.
\item Test with multiple taxonomic groups/ecosystems.  
\end{itemize}
\vspace{-7pt}
\begin{center}
\includegraphics[scale=.2]{./sad-data/dissertation/SpatialTaxonomic.png}
\end{center}
\end{frame}

\section{Data}
\subsection{Current Data}
\begin{frame}[t]
\frametitle{Current Data}
\vspace{-7pt}
\begin{center}
\includegraphics[scale=.45]{./sad-data/dissertation/ExistingDataMap.png}
\end{center}
\note{
\begin{large}
Major macroecological datasets\\
\end{large}
\begin{itemize}
\item Largely terrestrial
\item Largely North American
\item Many publicly available, some not.
\end{itemize}
~\\
~\\
~\\
~\\
\begin{large}
Lots of data in the literature.\\
\end{large}}
\end{frame}

@@

\subsubsection{Data Collection}
\begin{frame}[t]{}
\frametitle{Abundance database}
Inclusion criteria:
\begin{itemize}
\item Quantitative abundances
\item Animals
\item Complete sampling
\item Must not be heavily summarized or processed
\item High degree of taxonomic resolution
\item Observational
\end{itemize}
\end{frame}

\begin{frame}[shrink=30]
\frametitle{Abundance database}
\begin{table}
\begin{tabular}{l} 
 Variables collected\\ 
\hline
\\
 Class \\
 Family\\
 Genus \\
 Species (Specific epithet)\\
 Relative abundance \\
 Abundance \\
 Collection Year, starting\\
 Collection Year, ending \\
 Site Name \\
 Biogeographic region \\
 Site notes\\ 
\end{tabular}
\caption{List of variables collected.}
\end{table}
\end{frame}

@@

\subsubsection{Data Summary}
\begin{frame}{}
\frametitle{Abundance database}
\includegraphics[scale=.35]{../Miscellaneous/Pictures/Phd/CompiledData.png}
\end{frame}

\begin{frame}{}
\frametitle{Abundance database}
\includegraphics[scale=.27]{./sad-data/dissertation/bioregions.png}
\end{frame}

\begin{frame}{}
\frametitle{Abundance database}
\includegraphics[scale=.45]{./sad-data/dissertation/taxa_sites.png}
\end{frame}

\begin{frame}{}
\frametitle{Abundance database}
\includegraphics[scale=.45]{./sad-data/dissertation/num_taxa.png}
\end{frame}

@@

\subsection{Analysis Data}
\begin{frame}{}
\frametitle{Data}
\begin{center}
\includegraphics[scale=.4]{./sad-data/dissertation/Database.png}
\end{center}
\end{frame}

\begin{frame}{}
\frametitle{Data}
\includegraphics[scale=.4]{./sad-data/dissertation/AllDatasets.png}
\end{frame}

@@

@@

\subsection{Conclusions}
\begin{frame}
\frametitle{Neutral analysis}
Difficult to identify a clear winning model.
\begin{itemize}
\item Results consistent with our species abundance distribution model comparisons. 
\item Results different from Connolly et al. 2014.
\begin{itemize}
\item May be biological mechanisms responsible for differences between marine and terrestrial communities.
\note{
\item Non-neutral model outperforms the neutral model in marine systems.
\item Our results suggest marine systems more generally approximated by non-neutral dynamics; terrestrial systems more variable between neutral and non-neutral dynamics.}
\end{itemize}
\end{itemize}
\end{frame}
